Summary of the Iberian Bees Database

### 2022-02-28 Manuscript/Summary/Summary.Rmd
Updates on summary stlii have to recover from master the author list

```{r echo=FALSE,eval=FALSE, message=FALSE, warning=FALSE}
#table of
#Name	
#Contact	
#Number of records as main dataholder	
#Number of records as co-dataholder
#email?? Maually :(
#default <- par()$mar
#par(mar = c(13.1, 4.1, 4.1, 2.1))
#barplot(head(sort(table(data2$Authors.to.give.credit), decreasing = TRUE),20), las = 2, cex.names = 0.7)
#par(mar = default)
#Can be done prettier.
#Ideally, we can merge all authors, split and count individually.
library(stringi)
authors <- data$Authors.to.give.credit[which(!is.na(data$Authors.to.give.credit))]
authors[which(authors == "Ornosa, C., Martínez, M. D.")] <- "C. Ornosa, M.D. Martínez"
authors[which(authors == "C. Ornosa & F. J. Ortiz-Sánchez")] <- "C. Ornosa, F. J. Ortiz-Sánchez"
authors[which(authors == "C. Ornosa & M.D. Martínez")] <- "C. Ornosa, M.D. Martínez"
authors[which(authors == "Ortiz-Sanchez, F.J.")] <- "F.J. Ortiz-Sanchez"
authors[which(authors == "Heras, C., Gayubo, S. F.")] <- "C. Heras, S.F. Gayubo"
authors[which(authors == "Ornosa, C.")] <- "C. Ornosa"
authors[which(authors == "Herrera, J.")] <- "Javier Herrera"
authors[which(authors == "Francisco Javier Ortiz-Sánchez, Pedro Coello & Manuel Baena")] <- "Francisco Javier Ortiz-Sánchez, Pedro Coello, Manuel Baena"
authors[which(authors == "González, J. A., Torres, F., Gayubo, S. F.")] <- "J.A. González, , F. Torres, S.F. Gayubo"
authors[which(authors == "Dardón, M. J., Torres, F., Asís, J. D.")] <- "M.J. Dardón, F. Torres, J.D. Asís"
authors[which(authors == "Pérez-Iñigo Mora, C.")] <- "C. Pérez-Iñigo Mora"
authors[which(authors == "Pablo Vargas, Concepción Ornosa, Francisco Javier Ortiz-Sánchez & Juan Arroyo")] <- "Pablo Vargas, Concepción Ornosa, Francisco Javier Ortiz-Sánchez, Juan Arroyo"
authors[which(authors == "C. Heras y S.F. Gayubo")] <- "C. Heras, S.F. Gayubo"
authors[which(authors == "J. L. BLANCO-PASTOR, C. ORNOSA, D. ROMERO, I. M. LIBERAL, J. M. GÓMEZ & P. VARGAS")] <- "J. L. Blanco-Pastor, C. Ornosa, D. Romero, I.M. Liberal, J.M. Gómez, P. Vargas"
authors[which(authors == "Concepción Ornosa, Félix Torres & Pilar de la Rúa")] <- "Concepción Ornosa, Félix Torres, Pilar de la Rúa"
authors[which(authors == "Castro, L.")] <- "L. Castro"
authors[which(authors == "Ortiz-Sanchez, F. J., Ornosa, C.")] <- "F.J. Ortiz-Sanchez, C. Ornosa"
authors[which(authors == "Banaszak, J., Ortiz-Sanchez, F. J.")] <- "J. Banaszak, F.J. Ortiz-Sanchez"
authors[which(authors == "C. Ornosa, F. Torres & F. J. Ortiz-Sánchez")] <- "C. Ornosa, F. Torres, F. J. Ortiz-Sánchez"

>>>>

```{r eval=FALSE, message=FALSE, warning=FALSE}
#table of
#Name	
#Contact	
#Number of records as main dataholder	
#Number of records as co-dataholder
#email?? Maually :(
#default <- par()$mar
#par(mar = c(13.1, 4.1, 4.1, 2.1))
#barplot(head(sort(table(data2$Authors.to.give.credit), decreasing = TRUE),20), las = 2, cex.names = 0.7)
#par(mar = default)
#Can be done prettier.
#Ideally, we can merge all authors, split and count individually.
library(stringi)
authors <- data$Authors.to.give.credit[which(!is.na(data$Authors.to.give.credit))]
authors[which(authors == "Ornosa, C., Martínez, M. D.")] <- "C. Ornosa, M.D. Martínez"
authors[which(authors == "C. Ornosa & F. J. Ortiz-Sánchez")] <- "C. Ornosa, F. J. Ortiz-Sánchez"
authors[which(authors == "C. Ornosa & M.D. Martínez")] <- "C. Ornosa, M.D. Martínez"
authors[which(authors == "Ortiz-Sanchez, F.J.")] <- "F.J. Ortiz-Sanchez"
authors[which(authors == "Heras, C., Gayubo, S. F.")] <- "C. Heras, S.F. Gayubo"
authors[which(authors == "Ornosa, C.")] <- "C. Ornosa"
authors[which(authors == "Herrera, J.")] <- "Javier Herrera"
authors[which(authors == "Francisco Javier Ortiz-Sánchez, Pedro Coello & Manuel Baena")] <- "Francisco Javier Ortiz-Sánchez, Pedro Coello, Manuel Baena"
authors[which(authors == "González, J. A., Torres, F., Gayubo, S. F.")] <- "J.A. González, , F. Torres, S.F. Gayubo"
authors[which(authors == "Dardón, M. J., Torres, F., Asís, J. D.")] <- "M.J. Dardón, F. Torres, J.D. Asís"
authors[which(authors == "Pérez-Iñigo Mora, C.")] <- "C. Pérez-Iñigo Mora"
authors[which(authors == "Pablo Vargas, Concepción Ornosa, Francisco Javier Ortiz-Sánchez & Juan Arroyo")] <- "Pablo Vargas, Concepción Ornosa, Francisco Javier Ortiz-Sánchez, Juan Arroyo"
authors[which(authors == "C. Heras y S.F. Gayubo")] <- "C. Heras, S.F. Gayubo"
authors[which(authors == "J. L. BLANCO-PASTOR, C. ORNOSA, D. ROMERO, I. M. LIBERAL, J. M. GÓMEZ & P. VARGAS")] <- "J. L. Blanco-Pastor, C. Ornosa, D. Romero, I.M. Liberal, J.M. Gómez, P. Vargas"
authors[which(authors == "Concepción Ornosa, Félix Torres & Pilar de la Rúa")] <- "Concepción Ornosa, Félix Torres, Pilar de la Rúa"
authors[which(authors == "Castro, L.")] <- "L. Castro"
authors[which(authors == "Ortiz-Sanchez, F. J., Ornosa, C.")] <- "F.J. Ortiz-Sanchez, C. Ornosa"
authors[which(authors == "Banaszak, J., Ortiz-Sanchez, F. J.")] <- "J. Banaszak, F.J. Ortiz-Sanchez"
authors[which(authors == "C. Ornosa, F. Torres & F. J. Ortiz-Sánchez")] <- "C. Ornosa, F. Torres, F. J. Ortiz-Sánchez"
